Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Clean up last sentence of abstract
Clean up motiviation in introduction

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Unfortunately the traditional method for rendering intersecting volumes using
hardware acceleration requires a large amount of geometry to be created every
frame.  In the simple case where two axis-aligned volumes intersect, it is shown
that Boolean operations can be used so that the camera may move without
regenerating any geometry.  Originally the two variations presented herein
still achieved similar frame rates.  However, after implementing early ray
termination, they have proven faster for typical data sets.
\end{abstract}

@@

With much of the original performance concerns alleviated, and more and more
data being collected from several different sources, researchers are again
looking at ways to effectively display multiple volumes simultaneously.  A few
different methods have been developed for rendering an arbitrary number of
volumes using hardware acceleration, but they can be problematic to implement,
rely on general-purpose GPU programming, or both.

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Unfortunately the traditional method for rendering intersecting volumes using
hardware acceleration requires a large amount of geometry to be created every
frame.  In the simple case where two axis-aligned volumes intersect, it is shown
that Boolean operations can be used so that the camera may move without
regenerating any geometry.  Originally the two variations presented herein
still achieved similar frame rates.  However, after implementing early ray
termination, they have proven to be faster for typical data sets.
\end{abstract}

@@

With much of the original performance concerns alleviated, and more and more
data being collected from several different sources, researchers are again
looking at ways to effectively display multiple volumes simultaneously.  A few
different methods have been developed for rendering an arbitrary number of
volumes using hardware acceleration, but they can be inefficient, problematic to
implement, or both.
